---
output:
  html_document:
    css: custom.css
  pdf_document: default
  word_document: default
---
```{r sources, echo=F}
  library(pander)
  source('~/Dropbox/R/Quarterly Reports/Output/Quarterly_Report.R')
  options(scipen=999)
```
<!--- Name of Current Company. Set in the Quarterly_Report.R file. -->
# `r Company`

<!--- Output the number of unique orders, the sum of all the non-new order's revenue, and the average revenue across those orders. -->
## Orders: `r nrow(unique(orders))`
### Approximate Potential Revenue: $`r format(round(sum(orders[orders$Status != 'rejected', 'Potential.Revenue'])/100, 2), nsmall = 2)`
### Approximate Revenue Per Order: $`r format(round(sum(orders[!(orders$Status %in% c('new', 'rejected')), 'Potential.Revenue'])/100/nrow(unique(orders[!(orders$Status %in% c('new', 'rejected')),])), 2), nsmall = 2)`
```{r orders.items.table, echo=FALSE, comment=NA}
  row.names(orders.items.table) <- NULL
  pander(orders.items.table, justify = c('left', 'right'))
```
```{r order.status,  fig.width=7, fig.height=4, echo=FALSE}
  orders.status.chart
```
```{r orders.status.table, echo=FALSE, comment=NA}
  row.names(orders.status.table) <- NULL
  pander(orders.status.table.expanded, justify = c('left', 'center', 'right'))
```
```{r order.date.chart, fig.width=7, fig.height=4, echo=FALSE}
  orders.order.date.chart
```
```{r order.revenue.date.chart, fig.width=7, fig.height=4, echo=FALSE}
  orders.revenue.date.chart
```

---

## Patients: `r nrow(unique(patients))`
```{r echo=FALSE}
  #NO TOUCHING
  working.patients <- patients
```
```{r patient.insurance, out.width=c('350px', '300px'), fig.show='hold', echo=FALSE}
  patients.insurance.chart
```
```{r patient.contact, out.width=c('350px', '300px'), fig.show='hold', echo=FALSE}
  patients.contact.type.chart
```  
```{r patient.insurance.type.table, echo=FALSE, comment=NA}
  row.names(patients.insurance.type.table) <- NULL
  pander(patients.insurance.type.table, justify = c('left', 'right'))
```
```{r patient.contact.type.table, echo=FALSE, comment=NA}
  row.names(patients.contact.type.table) <- NULL
  pander(patients.contact.type.table, justify = c('left', 'right'))
```

---

## New Patients: `r nrow(unique(new.patients))`
```{r echo=FALSE}
  #NO TOUCHING
  working.patients <- new.patients
```
```{r new.patient.insurance, out.width=c('350px', '300px'), fig.show='hold', echo=FALSE}
    if(nrow(unique(new.patients)) > 0) {
      new.patients.insurance.chart
    }
```
```{r new.patient.contact, out.width=c('350px', '300px'), fig.show='hold', echo=FALSE}
    if(nrow(unique(new.patients)) > 0) {
      new.patients.contact.type.chart
    }
```
```{r new.patient.insurance.type.table, echo=FALSE, comment=NA}
  if(nrow(unique(new.patients)) > 0) {
    row.names(new.patients.insurance.type.table) <- NULL
    pander(new.patients.insurance.type.table, justify = c('left', 'right'))
  }
```
```{r new.patient.contact.type.table, echo=FALSE, comment=NA}
  if(nrow(unique(new.patients)) > 0) {
    row.names(new.patients.contact.type.table) <- NULL
    pander(new.patients.contact.type.table, justify = c('left', 'right'))
  }
```
```{r new.patients.eligibility, fig.width=7, fig.height=4, echo=FALSE}
    if(nrow(unique(new.patients)) > 0) {
      new.patients.eligibility.dates.chart
    }
```
---
